Cover Letter

### 2020-03-25 defesa/article/article.tex
wip

\RequirePackage{algorithm, algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\algorithmautorefname}{Algorithm}
\newcommand{\definitionautorefname}{Definition}
\newcommand{\thmautorefname}{Theorem}
\newcommand{\prpautorefname}{Proposition}
\newcommand{\lemmaautorefname}{Lemma}
\newcommand{\lemautorefname}{Lemma}

@@

		\title{Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}}
		\tnotetext[t1]{This paper is the results of the research
			project funded by CAPES.}

@@

		%\address{Department of Applied Mathematics and Statistics, Institute of Mathematical and Computer Sciences, University of São Paulo, Avenida Trabalhador São-carlense, 400, Centro, 13566-590, São Carlos, SP, Brazil.}
		%\author{John Smith}

@@

		\begin{keyword}
			Optimization \sep Covering \sep Combinatorial Optimization
			%% keywords here, in the form: keyword \sep keyword

@@

\section{An algorithm for MCE}\label{section:mce}

@@

\section{Determining every center and angle of rotation of an ellipse given its shape and three points that it must contain}\label{section:e3p}

>>>>

\RequirePackage{algorithm, algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\algorithmautorefname}{Algorithm}
\newcommand{\definitionautorefname}{Definition}
\newcommand{\thmautorefname}{Theorem}
\newcommand{\prpautorefname}{Proposition}
\newcommand{\lemmaautorefname}{Lemma}
\newcommand{\lemautorefname}{Lemma}
\newcommand{\sigla}[2]{#2 (#1)}
\newcommand{\citeonline}[1]{\cite{#1}}

@@

		\title{New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}}
		\tnotetext[t1]{This paper is the results of the research
			project funded by CAPES and FAPESP.}

@@

		\address{Department of Applied Mathematics and Statistics, Institute of Mathematical and Computer Sciences, University of São Paulo, Avenida Trabalhador São-carlense, 400, Centro, 13566-590, São Carlos, SP, Brazil.}
		%\author{John Smith}

@@

		\begin{keyword}
			Combinatorial optimization \sep planar maximal covering location problem \sep planar covering by ellipses \sep exact algorithms.
			%% keywords here, in the form: keyword \sep keyword

@@

\section{An Algorithm for MCE}\label{section:mce}

@@

\section{Determining Every Center and Angle of Rotation of An Ellipse Given Its Shape and Three Points that It Must Contain}\label{section:e3p}

### 2020-03-25 defesa/article/conclusion.tex
wip

In this work, we developed new algorithms for two planar maximum covering by ellipses problems.
After some improvements suggestions were given, numerical experiments were conducted showing the efficiency of both algorithms for instances from previous works and for new ones with larger demand and facility sets.

We devoted most of our work to the development of an exact algorithm for the version of the problem where the ellipses can be freely rotated.
In the midst of that, a never-studied-before subproblem came up, for which we also proposed an algorithm involving determining the roots of a complex polynomial.
Our algorithm for this version of the problem was able to obtain optimal solutions for instances which the heuristic method developed in \cite{andreta} returned non-optimal ones, and the deterministic method timed out.

We believe that the never-studied-before subproblem, which was the subject of \autoref{section:e3p}, has some properties that we were not able to explore, which could be the subject of future work. 
We observed that the solutions, except for one case, always come in pairs; and that the generated complex polynomial whose roots provide solutions for the problem appears to be a self-inverse polynomial.

>>>>

In this work, we developed new algorithms for two planar maximum covering by ellipses problems.
After giving improvements suggestions, and implementation details, we analyzed numerical experiments showing the efficiency of both algorithms for the instances of previous works, and for new ones with larger demand and facility sets.

We devoted most of our work to the development of an exact algorithm for MCER.
In the midst of that, a never-studied-before subproblem came up, for which we also proposed an algorithm, which involved determining the roots of a complex polynomial of degree six.
We believe that further exploring this new problem could be the subject of future work as we observed that its solutions, except for one case, always come in pairs; and that this property seems to be directly connected with the complex polynomial, as its roots seem to come in conjugate pairs. These properties, if proved to be true, might be used in the development of a more efficient algorithm.

### 2020-03-25 defesa/article/cover.tex
wip

\documentclass[3p, 11pt]{elsarticle}

@@

\journal{EJOR}

\usepackage[mathscr]{eucal}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Co}{\mathbb{Co}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\Pp}{\mathscr{P}}
\newcommand{\Cc}{\mathscr{C}}
\newcommand{\E}{\mathscr{E}}
\newcommand{\F}{\mathscr{F}}
\newcommand{\Ww}{\mathscr{W}}
\newcommand{\Rr}{\mathscr{R}}
\newcommand{\norm}[2][2]{\left\lVert#2\right\rVert_{#1}}
\newcommand{\bigO}{\mathscr{O}}
\newtheorem{thm}{Theorem}
\newtheorem{prp}{Proposition}
\newtheorem{lem}{Lemma}
\newdefinition{rmk}{Remark}
\newdefinition{definition}{Definition}
%\newproof{pf}{Proof}
%\renewcommand\qedsymbol{$\blacksquare$}

@@

\begin{document}

	\begin{frontmatter}

		%% Title, authors and addresses

		\title{New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}}
		\tnotetext[t1]{This paper is the results of the research
			project funded by CAPES and FAPESP.}

		%% use the tnoteref command within \title for footnotes;
		%% use the tnotetext command for the associated footnote;
		%% use the fnref command within \author or \address for footnotes;
		%% use the fntext command for the associated footnote;
		%% use the corref command within \author for corresponding author footnotes;
		%% use the cortext command for the associated footnote;
		%% use the ead command for the email address,
		%% and the form \ead[url] for the home page:
		%%
		%% \title{Title\tnoteref{label1}}
		%% \tnotetext[label1]{}
		%% \author{Name\corref{cor1}\fnref{label2}}
		%% \ead{email address}
		%% \ead[url]{home page}
		%% \fntext[label2]{}
		%% \cortext[cor1]{}
		%% \address{Address\fnref{label3}}
		%% \fntext[label3]{}

		%% use optional labels to link authors explicitly to addresses:
		%% \author[label1,label2]{<author name>}
		%% \address[label1]{<address>}
		%% \address[label2]{<address>}

		\author[1]{Danilo Tedeschi}
		\ead{danilo.tedeschi@usp.br}

		\author[2]{Marina Andretta}
		\ead{andretta@gmail.com}

		\address{Department of Applied Mathematics and Statistics, Institute of Mathematical and Computer Sciences, University of São Paulo, Avenida Trabalhador São-carlense, 400, Centro, 13566-590, São Carlos, SP, Brazil.}
		%\author{John Smith}

		%address{California, United States}

		\begin{abstract}
			%% Text of abstract
			Planar Maximum Covering Location by Ellipses is an optimization problem where one wants to place fixed shape ellipses on the plane to cover demand points
			maximizing a function depending on the value of covered points.
			We propose new exact algorithms for two versions of this problem, one where the ellipses have to be parallel to the coordinate axis, and another where they can be freely rotated. 
			Besides finding optimal solutions for previously published instances, including the ones where no optimal solution was known, both algorithms proposed by us were able to obtain optimal solutions for some new larger instances 	with up to seven hundred demand points and five ellipses.
		\end{abstract}

		\begin{keyword}
			Combinatorial optimization \sep planar maximal covering location problem \sep planar covering by ellipses \sep exact algorithms.
			%% keywords here, in the form: keyword \sep keyword

			%% MSC codes here, in the form: \MSC code \sep code
			%% or \MSC[2008] code \sep code (2000 is the default)

		\end{keyword}

	\end{frontmatter}

\section{Introduction}\label{section:introduction}

\input{introduction.tex}

\section{Definition}\label{section:definition}
\input{definition.tex}

\section{An Algorithm for MCE}\label{section:mce}

\input{mce.tex}

\section{Determining Every Center and Angle of Rotation of An Ellipse Given Its Shape and Three Points that It Must Contain}\label{section:e3p}

\input{e3p.tex}

\section{An Algorithm for MCER}\label{section:mcer}

\input{mcer.tex}

\section{Improvements}\label{section:improvements}
\input{improvements.tex}

%\section{Reducing the CLS size}\label{section:reducing_cls}
%\input{reducing_cls.tex}

%\section{Prunning the Backtracking Tree}\label{section:prunning}
%\input{prunning.tex}

\section{Implementation Details}\label{section:implementation}
\input{implementation.tex}

\section{Numerical Experiments}\label{section:numerical}
\input{numerical.tex}

\section{Conclusion}\label{section:conclusion}
\input{conclusion.tex}

\clearpage
\section*{References}
	%% New version of the num-names style
	\bibliographystyle{elsarticle-num}
	\bibliography{../references}

@@

%%
%% End of file `elsarticle-template-1-num.tex'.

>>>>

\documentclass{article}

@@

%\journal{EJOR}

\usepackage[mathscr]{eucal}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Co}{\mathbb{Co}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\Pp}{\mathscr{P}}
\newcommand{\Cc}{\mathscr{C}}
\newcommand{\E}{\mathscr{E}}
\newcommand{\F}{\mathscr{F}}
\newcommand{\Ww}{\mathscr{W}}
\newcommand{\Rr}{\mathscr{R}}
\newcommand{\norm}[2][2]{\left\lVert#2\right\rVert_{#1}}
\newcommand{\bigO}{\mathscr{O}}
\newtheorem{thm}{Theorem}
\newtheorem{prp}{Proposition}
\newtheorem{lem}{Lemma}
%\newdefinition{rmk}{Remark}
%\newdefinition{definition}{Definition}
%\newproof{pf}{Proof}
%\renewcommand\qedsymbol{$\blacksquare$}

@@

\begin{document}
		\title{Cover Letter}
		\maketitle

		Dear Editor, we herewith submit the manuscript entitled New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems addressing two not-vastly-explored problems on which we could only find two published papers, with the most recent one being from seven years ago.

		We propose new algorithms for those two problems after proving that if the number of given ellipses is constant, an optimal solution is contained in a polynomial-sized set of solutions, transforming both problems in combinatorial optimization problems.

		We show that significant advances were accomplished both in theory and in practice by our work, and we believe that our manuscript is a strong match for this journal as, besides dealing with an optimization problem that has not been vastly studied, the most recent paper on this subject is published here.

		%\section*{References}
		%% New version of the num-names style
		%\bibliographystyle{elsarticle-num}
		%\bibliography{../references}

@@

### 2020-03-25 defesa/article/definition.tex
wip

To make the notation more clear, we define a solution of MCE as $Q:=(q_1, \dots, q_m)$, and a solution of MCER as $Q:=((q_1, \theta_1); \dots; (q_m, \theta_m))$. 
Let $w : A \subset \Pp \to \R$ be a function which takes a subset of the demand set and returns the sum of the weights of the points in $A$. Then, we define MCE  as the optimization problem 
\begin{equation*}
\max_{Q}  w\left(\cup_{j=1}^m\Pp \cap E_j(q_j)\right),
\end{equation*}
and similarly MCER as
\begin{equation*}
\max_{Q} w\left(\cup_{j=1}^m\Pp \cap E_j(q_j, \theta_j)\right).
\end{equation*}

We define an equivalence and a partial order relation between solutions of both MCE and MCER as follows.
Two solutions $Q$ and $Q'$ of MCE (MCER), are said to be equivalent to each other if
they both cover the same set of demand points.
% $\cup_{j=1}^m \Pp \cap E_j(q_j) = \cup_{j=1}^m \Pp \cap E_j(q_j')$ ($ \cup_{j=1}^m \Pp \cap E_j(q_j, \theta_j) = \cup_{j=1}^m \Pp \cap E_j(q_j', \theta_j')$). That is, two solutions are equivalent if they cover the same set of points.
We also define a partial order: $Q' \succ Q$ if, and only if the set of demand points covered in solution $Q$ is a subset of the demand points covered in solution $Q'$.

%if, and only if $\cup_{j=1}^m \Pp \cap E_j(q_j) \subset \cup_{j=1}^m \Pp \cap E_j(q_j')$ ($\Pp \cap\cup_{j=1}^m E_j(q_j, \theta_j) \subset \Pp \cap\cup_{j=1}^m E_j(q_j', \theta_j')$). That is, $Q' \succ Q$ if, and only if the set of points covered in solution $Q$ is a subset of the points covered in solution $Q'$.

%%% esse paragrafo ainda ta estranho.
Additionally, we denote by $\partial$ the boundary operator, for example, given an instance of MCE, $\partial E_1(q_1)$ represents the set of points $\{p \in \R^2\colon ||p-q_1||_{a_1,b_1,0} = 1\}$. Also, whenever we have an instance $(\Pp, \Ww, \{(a, b)\})$ with only one facility, we omit the index referring to the ellipse.

@@

In \cite{canbolat, andreta}, as a result of having costs assigned to each facility, two other parameters are present in the definition of the problem.
These new parameters are: the list of costs $\Cc=\{c_1, \dots, c_m\}$, with $c_j\in\R_{\ge0}$ being the $j$-th ellipse's cost; 
and an integer $k\in\mathbb{N}$, $k\le m$, which introduces a constraint requiring that exactly $k$ facilities have to be utilized.
Because of that, a solution also needs an additional parameter $I:=\{i_1, \dots, i_k\}\subset\{1, \dots, m\}$ to express the indexes of the utilized ellipses. We refer to this version of the problem as  MCE-$k$ and MCER-$k$.

@@

%Therefore, as this step can be seen as trivial, we focus on proposing algorithms for MCE and MCER, and in the section where we analyze the numerical experiments, as we use instances from \cite{andreta}, whenever we refer to an algorithm of MCE-$k$ (MCER-$k$), see it as an algorithm based on the approach described here, which uses $\binom{m}{k}$ instances of MCE (MCER) to obtain an optimal solution.

>>>>

To make the notation more clear, we define a solution of MCE as $Q:=(q_1, \dots, q_m)$, and a solution of MCER as $Q:=((q_1, \theta_1); \dots; (q_m, \theta_m))$. 
Let $w : A \subset \Pp \to \R$ be a function which takes a subset of the demand set and returns the sum of the weights of the points in $A$. Then, we define MCE  as the optimization problem 
\begin{equation*}
\max_{Q}  w\left(\bigcup_{j=1}^m\Pp \cap E_j(q_j)\right),
\end{equation*}
and similarly MCER as
\begin{equation*}
\max_{Q} w\left(\bigcup_{j=1}^m\Pp \cap E_j(q_j, \theta_j)\right).
\end{equation*}

@@

In \cite{canbolat, andreta}, as a result of having costs assigned to each facility, two other parameters are present in the definition of the problem.
These new parameters are: the list of costs $\Cc:=\{c_1, \dots, c_m\}$, with $c_j\in\R_{\ge0}$ being the $j$-th ellipse's cost; 
and an integer $k\in\mathbb{N}$, $k\le m$, which introduces a constraint requiring that exactly $k$ facilities have to be utilized.
Because of that, a solution also needs an additional parameter $I:=\{i_1, \dots, i_k\}\subset\{1, \dots, m\}$ to express the indexes of the utilized ellipses. We refer to this version of the problem as  MCE-$k$ and MCER-$k$.

@@

\subsection{Additional Notation}

%Let $Q$ and $Q'$ be two solutions of MCE or MCER, we define two relations between solutions:
%\begin{itemize}
	%\item $Q$ is equivalent to $Q'$ if, and only if the set of covered demand points in both solutions is the same.
	%\item $Q' \succ Q$ if, and only if the set of demand points covered in solution $Q$ is a subset of the demand points covered in solution $Q'$.
%\end{itemize}

We define an instance of the one-facility MCE or MCER as $(\Pp, \Ww, \{(a,b)\})$ omitting the facility index in every notation. For example, a solution of MCER is denoted as $Q := (q, \theta)$.

Two solutions $Q$ and $Q'$ of MCE or MCER are said to be equivalent to each other if
the set of covered demand points in both solutions is the same.
We also define a partial order: $Q' \succ Q$ if, and only if the set of demand points covered in solution $Q$ is a subset of the demand points covered in solution $Q'$.

%%% esse paragrafo ainda ta estranho.
We use the notation $\partial$ to denote the boundary operator. For example, let $E \colon \R^2\to\R^2$ be the coverage region of an axis-parallel ellipse, then let $q\in\R^2$, $\partial E(q)$ describes an axis-parallel ellipse centered at $q$. If $E$ has shape parameters $(a, b)$, then $\partial E(q) = \{p \in \R^2\colon ||p-q||_{a,b,0} = 1\}$.

%Also, whenever we have an instance $(\Pp, \Ww, \{(a, b)\})$ with only one facility, we omit the index referring to the ellipse. 
%Therefore, as this step can be seen as trivial, we focus on proposing algorithms for MCE and MCER, and in the section where we analyze the numerical experiments, as we use instances from \cite{andreta}, whenever we refer to an algorithm of MCE-$k$ (MCER-$k$), see it as an algorithm based on the approach described here, which uses $\binom{m}{k}$ instances of MCE (MCER) to obtain an optimal solution.

### 2020-03-25 defesa/article/e3p.tex
wip

Given the shape parameters of an ellipse $(a, b)$, $a > b >0$, and three points $u, v, w \in \R^2$, let $E\colon \R^2\times [0, \pi)\to\R^2$ be the coverage region of an ellipse with shape parameters $(a, b)$, we refer to the problem of obtaining $(q, \theta) \in \R^2\times [0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$ as Ellipse by Three Points Problem (E3P).
Because of its application here in our work, we are only interested in a method that can obtain every solution of E3P.

>>>>

Given the shape parameters of an ellipse $(a, b) \in \R^2_{>0}$, $a > b$, and three points $u, v, w \in \R^2$, let $E\colon \R^2\times [0, \pi)\to\R^2$ be the coverage region of an ellipse with shape parameters $(a, b)$, we refer to the problem of obtaining $(q, \theta) \in \R^2\times [0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$ as Ellipse by Three Points Problem (E3P).
Because of its application here in our work, we are only interested in a method that can obtain every solution of E3P.

### 2020-03-25 defesa/article/introduction.tex
wip

The Planar Maximum Covering Location Problem (PMCLP) was first introduced in \cite{church:1984}, and can be seen as a category of problems where the coverage of a demand set, a collection of subsets of $\R^2$, is to be maximized by determining the location of facilities in $\R^2$, with coverage being determined by a distance function.
In \cite{church:1984}, methods for Euclidean and Rectilinear distances versions of the problem were proposed.
In \cite{drezner, chazelle:1986}, exact algorithms for the Euclidean PMCLP with only one facility are proposed; and in \cite{cabello:2006} an approximation algorithm is proposed for the version with multiple unit disks as facilities.
A property of the Euclidean PMCLP, which is utilized in the algorithms developed in \cite{drezner, chazelle:1986, cabello:2006}, and in the method proposed in \cite{church:1984}, is that there is an optimal solution which every facility is located in the demand points, or in the intersection of two circles centered at two demand points; we will prove a similar property for ellipses in our work.

It is fair to say that PMCLP with elliptical coverage has not been vastly studied as only two articles have been found on it. In \cite{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to the problem. For some instances, the method took too long and did not find an optimal solution. Because of that, a heuristic method was developed using a technique called Simulated Annealing, which was able to obtain solutions for the instances proposed in that study.
The problem was further explored in \cite{andreta}, which introduced the version where the ellipses can be freely rotated, to which an exact and a heuristic method was proposed, and developed a new method for the axis-parallel version of the problem, which was able to obtain optimal solutions for instances that the method proposed by \cite{canbolat} could not.
The exact method for the version with rotation could not obtain optimal solutions within a predefined time limit for several instances, the heuristic method though returned solutions for every instance, and impressively enough, obtained optimal solutions for every verifiable instance.

We study two versions of PMCLP with elliptical coverage facilities in this work. For both of them, each ellipse is defined to have a fixed shape and an undefined location, which is part of the solution.
In the first version, introduced in \cite{canbolat}, all the ellipses are restricted to be axis-parallel, while in the second version, introduced in \cite{andreta}, this constraint is dropped, and all the ellipses can be freely rotated.
The first version will be referred to as Planar Maximum Covering Location by Ellipses Problem (MCE) and the second one as  Planar Maximum Covering Location by Ellipses with Rotation Problem (MCER).

>>>>

\sigla{MCLP}{The Maximum Covering Location Problem}, introduced in \cite{church:1974}, is 
a problem defined on graphs where the objective is to maximize the coverage of a demand set, a subset of the graph's vertices, by choosing the location of a fixed number of facilities, with each facility covering every demand node located within a predefined radius from it. 
MCLP was introduced motivated by the practical observation that covering one hundred percent of a population, which was the subject of most of the covering location problems at that time, can take much more resources than covering ninety percent of it.

A continuous extension of MCLP, where the facility and demand sets are located on the plane and coverage is determined by a norm function, was introduced in \cite{church:1984} and named \sigla{PMCLP}{Planar Maximal Covering Location Problem} following the advances on covering location problems on the plane that were being made at the time.

PMCLP can be seen as a class of problems, as, in general, facilities can have their coverage defined by any norm function, and the demand set, although initially defined as points, could have a more generic definition; in \cite{bansal}, for example, they are defined as rectangles.
In \cite{church:1984}, a method was proposed for the version of PMCLP, where the facilities have Euclidean norm coverage. This method consisted of obtaining a discrete set of solutions for each facility, which was proved to contain at least one optimal solution, and then using the model developed for MCLP in \cite{church:1974} to determine an optimal solution.

The Euclidean PMCLP is also found in the literature in an algorithmic context as the \sigla{MCD}{Maximum Covering by Disks Problem}.
In \citeonline{chazelle:1986}, a $\bigO(n^2)$ algorithm for the one-disk version of MCD was proposed, beating the prior $\bigO(n^2\log{n})$ algorithm created in \citeonline{drezner} for the same problem.
A version with multiple unit disks was studied in \citeonline{cabello:2006}, which had as its most important result a $(1-\epsilon)$-approximation algorithm which runs in $\bigO(n\log{n})$. To achieve its main goal, they developed a deterministic $\bigO(n^{2m-1}\log{n})$ algorithm which gets employed into their approximation scheme.
Additionally, in \citeonline{aronov:2008}, one-disk MCD is proven to be 3SUM-HARD. This means that maximizing the number of points covered by a disk is as hard as finding three real numbers that sum to zero among $n$ given real numbers.

We study two versions of PMCLP with elliptical coverage facilities in this work. For both of them, each ellipse is defined to have a fixed shape and an undefined location, which is part of the solution.
In the first version, introduced in \cite{canbolat}, all the ellipses are restricted to be axis-parallel, while in the second version, introduced in \cite{andreta}, this constraint is dropped, and all the ellipses can be freely rotated.
The first version will be referred to as \sigla{MCE}{Planar Maximum Covering Location by Ellipses Problem} and the second one as  \sigla{MCER}{Planar Maximum Covering Location by Ellipses with Rotation Problem}.

It is fair to say that PMCLP with elliptical coverage has not been vastly studied as only two articles have been found on it. In \citeonline{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to MCE. For some instances, the method took too long and did not find an optimal solution.
Because of that, a heuristic method was developed using a technique called Simulated Annealing, which was able to obtain solutions for the instances proposed in that study.

The problem was further explored in \citeonline{andreta}, where exact methods were developed for both MCE and MCER, and a heuristic method was developed for MCER.
All the methods proposed in \cite{andreta} were based on the enumerative approach of solving optimization subproblems to determine whether an ellipse could cover a subset of demand points or not. To avoid having to solve subproblems for every subset of demand points, a tree-like data structure was designed to skip non-maximal sets of demand points.
The only difference in their methods for MCE and MCER was the subproblem.
As the subproblem for MCE was a convenient convex optimization model, the method for it performed well and  was able to obtain optimal solutions for instances the method from \cite{canbolat} could not.
The subproblem for MCER, on the other hand, was more challenging, and ended up making the method time out for large instances. For this reason, a heuristic method was developed treating the optimization subproblem as a convex problem. The method was able to obtain solutions for every instance, and for the ones the exact method did not time out, it could be verified that the heuristic method returned optimal solution as well.

Based on the developments of \cite{church:1984} for the Euclidean PMCLP, we define a finite set of solutions for each one of the problems, MCE and MCER, which we prove to contain at least one optimal solution, and that, if the number of facilities is assumed to be constant, its size is bounded by a polynomial.
We propose algorithms for both problems based on the computation of this set of solutions to determine an optimal one.
For MCER, computing this set of solutions involves solving a subproblem, on which we could not find any prior study, thus, a whole section is devoted to the development of an algorithm for it.
Besides all that, we give implementation details for both algorithms, and also improvement suggestions which, in practice, can significantly lower the number of solutions evaluated to return an optimal one.
In the end, we analyze numerical experiments for instances proposed in \cite{canbolat, andreta} and compare the results with the results obtained by the methods proposed in \cite{andreta}. Also, to further analyze our algorithms, we also analyzed numerical experiments for new instances with larger demand and facility sets.

### 2020-03-25 defesa/article/mce.tex
wip

\begin{prp}\label{lema:mce-mwc}
	Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE, and $q\in \R^2$. If $\Pp \cap E(q) = A$, then $q \in \cap_{p\in A} E(p)$ and for any $q' \in \cap_{p\in A} E(p)$, we have $A \subset E(q')$.
\end{prp}
\begin{proof}
	Let $u, v \in \R^2$, then we have the following equivalence:
	\begin{equation}\label{eq:peq}
	u \in E(v) \Leftrightarrow ||u-v||_{a, b, 0} \le 1 \Leftrightarrow v \in E(u).
	\end{equation}
	Therefore, if $p\in A$, by \autoref{eq:peq}, then $q \in E(p)$, which implies $q \in \cap_{p\in A} E(p)$.
	The second part of the lemma also follows from \autoref{eq:peq}. If $q' \in \cap_{p\in A} E(p)$, then $||q' - p||_{a,b,0} \le 1$ for all $p \in A$.
\end{proof}

@@

\begin{lem}\label{lema:mce}
	Let $q\in \R^2$ be a solution of MCE for the instance $(\Pp, \Ww, \{(a, b)\})$.
	If $|\Pp \cap E(q)|\ge 2$, then there exists $q' \in \cup_{u, v \in \Pp}\partial E(u) \cap \partial E(v)$, such that $q' \succ q$.
\end{lem}
\begin{proof}
	By \autoref{lema:e2p}, let $A=\Pp \cap E(q)$, we have that for any $q' \in \cap_{p\in A} E(p)$, $q' \succ q$. 
	Furthermore, by the results of \cite{bi}, we have that there exists $q' \in \cup_{u, v \in A}\partial E(u) \cap \partial E(v)$, such that $q' \in \cup_{p\in A} E(p)$. 
	Therefore, $q' \in \cup_{u, v \in \Pp}\partial E(u) \cap \partial E(v)$, and $q' \succ q$.
\end{proof}

>>>>

%\begin{prp}\label{lema:mce-mwc}
%	Let $(\Pp, \Ww, \{(a, b)\})$ be an instance of MCE, and $q\in \R^2$. If $\Pp \cap E(q) = A$, then $q \in \cap_{p\in A} E(p)$ and for any $q' \in \cap_{p\in A} E(p)$, we have $A \subset E(q')$.
%\end{prp}

\begin{prp}\label{lema:mce-mwc}
	Let $q\in \R^2$ be a solution of the one-facility MCE. If $\Pp \cap E(q) = A$, then $q \in \cap_{p\in A} E(p)$ and for any $q' \in \cap_{p\in A} E(p)$, we have $A \subset E(q')$.
\end{prp}
\begin{proof}
	Let $u, v \in \R^2$, then we have the following equivalence:
	\begin{equation}\label{eq:peq}
	u \in E(v) \Leftrightarrow ||u-v||_{a, b, 0} \le 1 \Leftrightarrow v \in E(u).
	\end{equation}
	Therefore, if $p\in A$, by \autoref{eq:peq}, then $q \in E(p)$, which implies $q \in \cap_{p\in A} E(p)$.
	The second part of the lemma also follows from \autoref{eq:peq}. If $q' \in \cap_{p\in A} E(p)$, then $||q' - p||_{a,b,0} \le 1$ for all $p \in A$.
\end{proof}

@@

\begin{lem}\label{lema:mce}
	Let $q\in \R^2$ be a solution of the one-facility MCE.
	If $|\Pp \cap E(q)|\ge 2$, then there exists $q' \in \cup_{u, v \in \Pp}\partial E(u) \cap \partial E(v)$, such that $q' \succ q$.
\end{lem}
\begin{proof}
	By \autoref{lema:e2p}, let $A=\Pp \cap E(q)$, we have that for any $q' \in \cap_{p\in A} E(p)$, $q' \succ q$. 
	Furthermore, by the results of \cite{bi}, we have that there exists $q' \in \cup_{u, v \in A}\partial E(u) \cap \partial E(v)$, such that $q' \in \cup_{p\in A} E(p)$. 
	Therefore, $q' \in \cup_{u, v \in \Pp}\partial E(u) \cap \partial E(v)$, and $q' \succ q$.
\end{proof}
